Xor-Some Preregistered Study: Analyses

### 2021-11-10 analysis/main/01_xor-some_prereg_preprocessing_final.Rmd
rerun analyses on updated N200, add priors exploration

@@

@@

cat(" Nr. of participants left after cleaning: ", d_full_clean %>% distinct(submission_id) %>% pull() %>% length())
```
Exclude the 201st participant for target N=200:
```{r, results='hide'}
d_full_clean %>% arrange(., desc(submission_id)) %>% distinct() %>% pull(submission_id)

# exclude participant with last submission_id
d_full_clean <- d_full_clean %>% filter(submission_id != 2620)

@@

d_critical_zScored_wide <- d_critical_zScored %>% 
  select(submission_id, title, main_type, block_extended, response_centered) %>% 
  unique() %>% 
  pivot_wider(
    names_from = block_extended, 
    values_from = response_centered, 
    values_fn = mean # getting means for double prior measurement in "xor"
  ) 
```

>>>>

d_native %>% distinct(languages)

@@

Perform an alternative exclusion based on comprehension question EXCLUDING the test_false1 question from the vignette with the ID=64 which had an incorrect prior classification.
```{r}
# get participants failing comprehension questions
d_test_alternative <- d_test %>%
  group_by(submission_id) %>%
  filter(ID != 64 && test_question != "test_false1") %>%
  mutate(passed_filler_trial = case_when(test_condition == "true" ~ response >= 60,
                                   test_condition == "false" ~ response <= 40,
                                   test_condition == "uncertain" ~ response %in% (10:90)),
         mean_comprehension = mean(passed_filler_trial),
         passed_filler = mean_comprehension >= 0.8
         )

d_test_fail_alternative <- d_test_alternative %>% 
  filter(passed_filler == F)

cat(" Subjects failing the comprehension trials without misclassified trial: ", d_test_fail_alternative %>% distinct(submission_id) %>% pull() %>% length())
```

@@

cat(" Nr. of participants left after cleaning: ", d_full_clean %>% distinct(submission_id) %>% pull() %>% length())
```
[-Exclude the 201st participant for target N=200-]
The exclusion of the last participant isn't necessary anymore, since we only have 200 subjects left upon exclusions due to the initially incorrect native language check.
```{r, results='hide'}
#d_full_clean %>% arrange(., desc(submission_id)) %>% distinct() %>% pull(submission_id)

# exclude participant with last submission_id
#d_full_clean <- d_full_clean %>% filter(submission_id != 2620)

@@

d_critical_zScored_wide <- d_critical_zScored %>% 
  select(submission_id, title, main_type, block_extended, response_centered) %>% 
  unique() %>% 
  pivot_wider(
    names_from = block_extended, 
    values_from = response_centered, 
    values_fn = mean # getting means for double prior measurement in "xor"
  )

# write out a wide df with both prior ratings for exploratory analysis
d_critical_zScored_xor <- d_critical_zScored %>% 
  ungroup() %>%
  select(submission_id, title, main_type, block_extended, response_centered) %>% 
  unique() %>% 
  filter(main_type == "xor")

d_critical_zScored_wide_xor_priors <- d_critical_zScored_xor %>% group_by(title, block_extended) %>% 
  mutate(
    block_extended = ifelse(block_extended == "prior", 
                            paste(block_extended, which(block_extended == "prior")%%2, sep="_"),
                            block_extended)
  ) %>% ungroup() %>%
  pivot_wider(
    names_from = block_extended, 
    values_from = response_centered 
  ) %>%
  filter(!is.na(prior_1), !is.na(prior_0)) # not sure where the NAs came from

## no idea why it didn't work with just pivot_wider(names_from = block_extended, values_from = response_centered, names_repair = "unique")

d_critical_zScored_wide_xor_priors %>% write_csv("./../../data/main/results_prereg_tidy_final_zScored_wide_xor_priors.csv")
```

### 2021-11-10 analysis/main/03_xor-some_prereg_analysis_final.Rmd
rerun analyses on updated N200, add priors exploration

Read data created in preprocessing script:
```{r, message=FALSE, warning=FALSE, results='hide'}
d_critical_zScored_wide <- read_csv("./../../data/main/results_prereg_tidy_final_zScored_wide.csv")
d_critical_zScored <- read_csv("./../../data/main/results_prereg_tidy_final_zScored_long.csv")
```

@@

>>>>

Read data created in preprocessing script:
```{r, message=FALSE, warning=FALSE, results='hide'}
d_critical_zScored_wide <- read_csv("./../../data/main/results_prereg_tidy_final_zScored_wide.csv")
d_critical_zScored <- read_csv("./../../data/main/results_prereg_tidy_final_zScored_long.csv")
d_critical_zScored_wide_xor_priors <- read_csv("./../../data/main/results_prereg_tidy_final_zScored_wide_xor_priors.csv")
```

@@

A non-preregistered, but nevertheless possibly interesting exploratory analysis including the two individual prior ratings of the conditionals in the xor condition as predictors (as opposed to the mean of the two used in the preceding models):
```{r, results='hide', message=FALSE, warning=FALSE}

model_xor_priors <- brm(target ~ prior_0*prior_1*competence*relevance +
                   (1 + prior_0 + prior_1 + competence + relevance || submission_id) +
                   (1 | title),
                 data = d_critical_zScored_wide_xor_priors,
                 prior = priors,
                 sample_prior = T,
                 control = list(adapt_delta = 0.95),
                 cores = 4,
                 iter = 3000)
```

```{r}
summary(model_xor_priors)
```

Check the intervals of intervals, computing them separately using only one prior estimate, to see if we get different results:
```{r}
model_xor_priors %>% spread_draws(b_Intercept, b_prior_0, b_prior_1, b_competence, b_relevance) %>% 
  mutate(
    prior0_xor = b_prior_0,
    prior1_xor = b_prior_1,
    competence_xor = b_competence,
    relevance_xor =  b_relevance
  ) -> model_xor_priors_posteriors

# check P that the effects are positive / negative / no effect present
posterior_hypotheses_xor_priors <- model_xor_priors_posteriors %>% 
  select(prior0_xor, prior1_xor, 
         competence_xor, relevance_xor) %>%
  gather(key, val) %>%
  group_by(key) %>% mutate(positive = mean(val > 0.05),
                           negative = mean(val < -0.05),
                           no = mean(val %>% between(-0.05, 0.05))) %>%
  summarise(positive_eff = mean(positive),
            negative_eff = mean(negative),
            no_eff = mean(no))
posterior_hypotheses_xor_priors
```
